signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-16 paper.tex

The gain is not only a better fit to the data but also, as 
model structure (see figure \ref{fig:model_hsmm}) is straightforward, easier interpretation 
for researcher without mathematical background.

@@

HSMM can be further extend to use some specific motives that might occur in proximity of cleavage site.
Such an extension requires defining additional hidden states. 
It proves to be extremely useful in recognizing cleavage site.
Scheme can be seen in figure \ref{fig:model_hsmm_kMer}.

@@

n-grams (k-mers) are vectors of n characters derived from input sequences. They can be added as the new hidden state to the hidden semi-Markov model. The rigid structure of n-grams may mirror cleavage sites, whose are more conservative than other parts of signal peptide~\citep{2004hillerpredisi}.

>>>>

The gain is not only a better fit to the data but also, as 
model structure (see figure~\ref{fig:model_hsmm}) is straightforward, easier interpretation 
for researcher without mathematical background.

@@

@@

HSMM can be further extended to use some specific motives that might occur in proximity of cleavage site.
Such an extension requires defining additional hidden states. 
To find such motives we analyze n-grams (k-mers) -- vectors of n characters derived from input sequences. 
The rigid structure of n-grams may mirror cleavage sites, which are more 
conservative than other parts of signal peptide~\citep{2004hillerpredisi}.
Scheme of extended HSMM can be seen in figure~\ref{fig:model_hsmm_kMer}.
